Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2018-10-10 doc/network.tex
forgot to push

This perspective allows us to reinterpret the finding of \cite{trapman2016inferring} that, given an intrinsic generation interval and an observed growth rate $r$, the reproductive number $\RR$ on various network structures is always smaller on a network than would be predicted from homogeneous mixing.
\jd{Maybe moving on a good direction, but needs more work. The problem is that we need to talk clearly about the spatial correction without misleading people about the temporal correction.}

\swp{Will rewrite this paragraph after writing the rest of it:}
In this study, we explore the temporal and spatial variation in the observed generation-interval distributions obtained from contact tracing.
We show that using the observed generation-interval distribution directly will always underestimate the reproductive number \swp{need to confirm this statement when we're done with the ms}. 
We provide a statistical framework of recovering the intrinsic generation-interval distribution from the observed generation-interval distribution.

@@

\section{Statistical approach to inferring generation-interval distribution}

>>>>

This perspective allows us to reinterpret the finding of \cite{trapman2016inferring} that, given an intrinsic generation interval and an observed growth rate $r$, the reproductive number $\RR$ on various network structures is always smaller on a network than would be predicted from homogeneous mixing.
\jd{Maybe moving on a good direction, but needs more work. The problem is that we need to talk clearly about the spatial correction without misleading people about the temporal correction.}
\swp{Should we just talk about this in the paper rather than in intro? It feels like we're going into detail too much}

\swp{Will rewrite this paragraph after writing rest of the paper:}
In this study, we explore the temporal and spatial variation in the observed generation-interval distributions obtained from contact tracing.
We show that using the observed generation-interval distribution directly will always underestimate the reproductive number \swp{need to confirm this statement when we're done with the ms}. 
We provide a statistical framework of recovering the intrinsic generation-interval distribution from the observed generation-interval distribution.

@@

\section{Inferring generation-interval distributions from contact tracing data}

When generation intervals are sampled through contact tracing, there will be four effects present in the sample: (1) right-censoring effect, (2) egocentric effect, (3) local spatial effect and (4) global spatial effect.
Right-censoring effect and egocentric effect are well-understood and can be corrected for.
While local and global spatial effects are difficult to estimate, we can make qualitative predictions about their effects on the realized generation intervals and reproductive number. 
Both local and global effects reduce number of infections that occur and shorten generation intervals but the time scale on which they matter differ:
local spatial effect will be important early in an epidemic whereas the global effect will be small until after the exponential growth period has ended.
